---
title: "scRNAseq_to_ref"
output: html_document
date: "2026-02-15"
---

# scRNAseq to Reference


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


In this vignette, we aim to describe default process of FlexiDeconv to convert 
scRNAseq data to reference. The process uses three input datasets:
1. Spatial data with dimension pixel x gene
2. scRNAseq data with dimension cell x gene
3. Cell type annotation for every cell within scRNAseq, as a vector

For this vignette, we use the spatial data obtained from [@Moffitt2018DryadHypothalamus]
and scRNAseq data from [@NeMO_dat]. Note that the process described here is 
slightly different to the actual imperfect reference section in the paper, for 
the following purposes:
1. No redundant gene filtering was done in the actual paper, because the geneset 
size is already quite limited, there is no point to filter genes for speed 
purposes.
2. No variable gene selection was done in the actual paper, same reason as above.
3. The scRNAseq dataset only contains a small subset because the original dataset 
was too large.


Load in the libraries and data
```{r}
library(FlexiDeconv)
library(STdeconvolve)
library(ggplot2)
library(ggdist)
```

```{r}
data(scRNAseq_to_reference)
```

Spatial data sample (5 pixels x 5 genes)
Note that the rownames are simulated pixel barcodes.
```{r}
scRNAseq_to_reference$spatial[1:5,1:5]
```
scRNAseq data sample (5 cells x 5 genes)

```{r}
scRNAseq_to_reference$scRNAseqCount[1:5,1:5]
```

scRNAseq cell type data (5 cells)

```{r}
scRNAseq_to_reference$scRNAseqCellType[1:5]
```

# Step 1: human protein coding genes filter

Typically, for performing deconvolution on Spatial Transcriptomics data obtained
from human tissues, we would filter out non-human protein coding genes. However, 
since the current spatial data is from mouse, we do not perform such procedure.

For dataset size issues, we decide to leave this part blank and invite users to 
filter for human protein coding genes themselves.

# Step 2: find intersection gene set

Here we find interesection gene set between spatial data and scRNAseq data.

```{r}
common_geneset = commonGeneFilter(scRNAseq_to_reference$spatial,
                                  scRNAseq_to_reference$scRNAseqCount)
```

# Step 3: remove redundant genes

Here we remove redundant genes, defined as genes that have 0 counts across all 
pixels or across all cells. 

```{r}
remove_redundant = redundantGeneFilter(common_geneset$spatial, common_geneset$scRNAseq)
```


# Step 4: retain variable genes

Here we select variable genes using STdeconvolve's default gene selection method.
The purpose of step 4 is to reduce geneset size. Note that we only use spatial 
data for variable gene selection here.

Up to this point, spatial data is finalized.

```{r}
variableGenes = t(STdeconvolve::restrictCorpus(t(as.matrix(remove_redundant$spatial)), 
                                        removeAbove = 1.0,
                                        removeBelow = 0.01,
                                        alpha = 0.05,
                                        plot = F,
                                        verbose = T))
variableGenesData = list(spatial = variableGenes,
                         scRNAseq = remove_redundant$scRNAseq[,colnames(variableGenes)])


```

# Step 5: remove outlier cells

Finally, we remove outlier cells in scRNAseq data, with outlier cells defined as 
follows:
1. Cells with total gene count 1.5\*IQR above Q3 of all cells within *current cell type*.
2. Gene ranked _lowerThresholdRank_ (default 2) having less than _lowerThresholdCount_
counts (default 3). For example, under the current default setting, if the second 
highest gene count within a cell is below 3, then we remove this cell. It is motivated
by keep cells having sufficient count in the marker genes.

We also plot (rain cloud plot) the distribution of total read depth (total gene count) 
for every cell type.

```{r}
removeOutlierCells = outlierCellRemoval(variableGenesData$scRNAseq, 
                                        scRNAseq_to_reference$scRNAseqCellType,
                                        lowerThresholdRank = 2,
                                        lowerThresholdCount = 3)

```

# Step 6: form reference

Finally, we make reference by:
1. For every cell type, find all cells belonging to current cell type
2. Sum the raw gene counts across all cells
3. Normalize the overall gene count for this cell type such that the sum is 1.

```{r}
reference = formReference(removeOutlierCells$scRNAseq, removeOutlierCells$celltypes)
```

```{r}
visualizeReference(reference)
```




