---
title: "dataFinalProcessing_amended"
output: html_document
date: "2026-02-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import data + Libraries

```{r}
source("../functions(new).R")
library(VennDiagram)
library(Seurat)
library(STdeconvolve)
library(dplyr)

# isoform_reference = readRDS("../../Data/Isoform/LebrigandIsoform/references/GSE121891_unnormalized_ref_box.rds")
isoform_spatial = readRDS("../../Data/Isoform/LebrigandIsoform/GSE153859_MOB.rds")

# read count data
# gene (18560) x cell (51426)
# reference: cell x gene
raw_counts <- read.csv(file="../../Data/Isoform/LebrigandIsoform/GSE121891_OB_6_runs_processed_seurat.dge.csv")
isoform_reference = t(raw_counts)

# process metadata
# counts (51426) x information (8 types)
metadata<-read.table(file="../../Data/Isoform/LebrigandIsoform/GSE121891_OB_metaData_seurat.csv",sep=",", header=TRUE)
```

## Get different spatial data

```{r}
gene_shortread = t(isoform_spatial@assays$Spatial$counts) # 918 pixels x 31053 genes
gene_longread = t(isoform_spatial@assays$ISOG$counts) # 918 pixels x 18724 genes
isoform_longread = t(isoform_spatial@assays$ISO$counts) # 918 pixels x 23560 isoforms

## Question: Is he sure that this represents each row is a particular pixel? Their rownames 
##           seem more like DNA barcodes e.g. TTCGGGACTAATCGCG-1
## Answer: Yes it is the actual coordinates, can see via `isoform_spatial@images$slice1@coordinates`
## Follow up question: Why is coordinates represented in DNA barcode???

```

Diagnostic summary test to see if gene_LR counts are different to that of isoform_LR, if they are then it is due to QC differences.
Note: Does appear to be due to QC differences, that is ok and just be aware of gene_LR differences when comparing later with aggregated isoforM_LR,know that they are not the same thing
```{r}
# set.seed(1)
# genes = names(Filter(function(x) length(x) == 2, isoform_dict))
# sampled_genes = sample(genes, 10)
# 
# print(sampled_genes)
# 
# for (gene in sampled_genes){
#   iso_names = isoform_dict[[gene]]
#   gene_counts = gene_longread[, gene]
#   
#   iso1_col = paste0(gene, "..", iso_names[1])
#   iso2_col = paste0(gene, "..", iso_names[2])
#   
#   iso_sum = isoform_longread[, iso1_col] + isoform_longread[, iso2_col]
#   
#   # Table of gene-level counts
#   cat(paste0("\n Gene: ", gene))
#   cat("\nGene-level count table:\n")
#   print(table(gene_counts))
#   
#   # Table of aggregated isoform counts
#   cat("\nAggregated isoform count table:\n")
#   print(table(iso_sum))
# }
```


### Pre-step : Extracting gene names for each of Spatial, ISOG and ISO methods

```{r}
# Taking metafeatures of each SR, LR and isooform assay
spatial_genes = isoform_spatial@assays$Spatial@meta.features
isog_genes = isoform_spatial@assays$ISOG@meta.features
iso_isoform = isoform_spatial@assays$ISO@meta.features

# Filtering iso_genes to be gene name instead isoform
iso_isoform_rep = as.matrix(iso_isoform)
# Looking for just the gene names in the isoform level matrix
rownames(iso_isoform_rep) = sub("\\..*$", "", rownames(iso_isoform_rep))
iso_gene_list = unique(rownames(iso_isoform_rep))
```


## Step 2: Identify intersection of 2 gene sets ($C_{raw}$ and $R_{raw}$)
```{r}
# Calling the genes in reference tissue sample
reference_genes = colnames(isoform_reference)

# Find overlapping reference and SR spatial
spatial_overlap = intersect(reference_genes, rownames(spatial_genes))

# Find overlapping reference and LR gene
isog_overlap = intersect(reference_genes, rownames(isog_genes))

# Find overlapping reference and LR isoform
## Separates into effectively a 10000 long list of list of 2 elements: gene and isoform
## Structure: [[g1, g1i1], [g2, g2i1]]
## Note that: Note that multiple lists may have the same gene (not grouped together yet)]
## Output result: List of 11221 genes for 21013 isoforms 
isoform_dict = list()
rowname_sep = strsplit(rownames(iso_isoform), split = "\\.\\.")
gene_names = c()
isoform_names = c()
isoform_overlap = c()

'%notin%' <- function(x,y) !(x %in% y)

for (i in 1:length(rowname_sep)) {
  # Current gene name for this given isoform
  curr_g = rowname_sep[[i]][1]
  
  # Pseudo-equivalent of intersect(reference, ST data) as above
  if (curr_g %in% reference_genes) {
    if (curr_g %notin% gene_names){
      gene_names = c(gene_names, rowname_sep[[i]][1])
    }
    
    # Isoform dictionary[[]] Creates dictionary of all isoforms possessed by this current gene
    isoform_dict[[curr_g]] = c(isoform_dict[[curr_g]], rowname_sep[[i]][2])
    
    # List of all isoforms kept
    isoform_overlap = c(isoform_overlap, rownames(iso_isoform)[i])
  }
  # List of all isoforms
  isoform_names = c(isoform_names, rowname_sep[[i]][2])
}
```


## Step 3: For output gene sets in step 2, further remove genes that have 0 counts in all pixels in $C_{raw}$ or 0 counts across all cells in $R_{raw}$.
```{r}
# Gene SR
ST_expression_spatial <- colSums(as.matrix(gene_shortread[, spatial_overlap])) > 0
SC_expression_spatial <- colSums(as.matrix(isoform_reference[, spatial_overlap])) > 0

keep_genes = ST_expression_spatial & SC_expression_spatial
spatial_overlap_positive = spatial_overlap[keep_genes]

C_spatial = gene_shortread[, spatial_overlap_positive]
# R_spatial = isoform_reference[, spatial_overlap_positive]


# Gene LR
ST_expression_isog <- colSums(as.matrix(gene_longread[, isog_overlap])) > 0
SC_expression_isog <- colSums(as.matrix(isoform_reference[, isog_overlap])) > 0

keep_genes = ST_expression_isog & SC_expression_isog
isog_overlap_positive = isog_overlap[keep_genes]

C_isog = gene_longread[, isog_overlap_positive]
# R_isog = isoform_reference[, isog_overlap_positive]

# Isoform LR
ST_expression_iso <- colSums(as.matrix(isoform_longread[, isoform_overlap])) > 0

# Compressing to gene level for SC
SC_expression_gene = colSums(as.matrix(isoform_reference[, gene_names])) > 0
parent_genes = sub("\\..*$", "", isoform_overlap)
SC_expression_iso = SC_expression_gene[parent_genes]

keep_genes = ST_expression_iso & SC_expression_iso
isoform_overlap_positive = isoform_overlap[keep_genes]
gene_overlap_positive = unique(sub("\\..*$", "", isoform_overlap_positive))

C_iso = isoform_longread[, isoform_overlap_positive]
# R_iso = isoform_reference[, gene_overlap_positive]


##  Aggregating isoform -> gene level count data for restrictCorpus()
C_iso_rep = as.matrix(C_iso)
colnames(C_iso_rep) = sub("\\..*$", "", colnames(C_iso_rep))


C_iso_agg = matrix(0, nrow = nrow(isoform_longread), ncol = length(gene_overlap_positive))
rownames(C_iso_agg) = rownames(isoform_longread)
colnames(C_iso_agg) = gene_overlap_positive

for (gene in colnames(C_iso_rep)){
  # Summing adding all the columns in df that has the same gene colname together
  # Effectively adding vectors of dim 918 x 1 + 918 x 1 + ... -> Achieved via rowSum
  C_iso_agg[, gene] = rowSums(C_iso_rep[ ,which(colnames(C_iso_rep) == gene), drop=F])
}
```
Prepare to aggregate isoform counts data into gene counts data for variable gene selection.
Note that although this may miss genes where gene expression is constant but isoform switching occurs, this is rarely the case and not considered for now

## Step 4: For the output gene set in step 3, apply to Craw and perform variable gene selection. FlexiDeconv uses `restrictCorpus()` functions provided in STdeconvolve. We now have input ready C


```{r}
# Gene SR
spatial_selection <- t(restrictCorpus(t(C_spatial), plot = TRUE))
spatial_selected_genes = colnames(spatial_selection)

C_spatial_selection = gene_shortread[, spatial_selected_genes]

# Gene LR
isog_selection <- t(restrictCorpus(t(C_isog), plot = TRUE))
isog_selected_genes = colnames(isog_selection)

C_isog_selection = gene_longread[, isog_selected_genes]


# Isoform LR
##  Now de-aggregating the selected genes in `iso_selection` back to their isoform count form.
iso_selection <- t(restrictCorpus(t(C_iso_agg), plot = TRUE))

iso_selected_genes = colnames(iso_selection)
isoform_parent = sub("\\..*$", "", colnames(C_iso))
iso_selected_isoforms = colnames(C_iso)[isoform_parent %in% iso_selected_genes]

C_iso_selection = isoform_longread[, iso_selected_isoforms]
```

## Step 5: Modify $R_{raw}$ by removing cells with less than a total of 50 gene counts, also remove cell types (and all cells belonging to this cell type) having less than 25 cells. We denote the modified $R_{raw}$ as $R_{intermediate}$. These settings are referenced from RCTD’s software package.

```{r}
## Fix by putting filter after the gene
threshold_gene_count = 50
threshold_cell_count = 25

# # Remove any cells that have less than threshold_gene_count
# keep_cells = metadata$nUMI >= threshold_gene_count
# metadata = metadata[keep_cells, ]
# 
# # Remove any cell types that have less than threshold_cell_count
# celltype_count = table(metadata$ClusterName)
# keep_celltypes = names(celltype_count[celltype_count >= threshold_cell_count])
# metadata = metadata[metadata$ClusterName %in% keep_celltypes, ]

## Now applying to all the R_{raw} counts
# Gene SR
R_spatial_raw = isoform_reference[, spatial_selected_genes]
## Remove any cells that have less than threshold_gene_count
read_depth = rowSums(as.matrix(R_spatial_raw))
keep_cells = read_depth >= threshold_gene_count
R_spatial_raw = R_spatial_raw[keep_cells, ]

metadata_spatial <- metadata[metadata$X %in% rownames(R_spatial_raw), ]
celltype_count = table(metadata_spatial$ClusterName)
## Remove any cell types that have less than threshold_cell_count
keep_celltypes = names(celltype_count[celltype_count >= threshold_cell_count])
metadata_spatial = metadata_spatial[metadata_spatial$ClusterName %in% keep_celltypes, ]
R_spatial_selection = R_spatial_raw[metadata_spatial$X, ]

# Gene LR
R_isog_raw = isoform_reference[, isog_selected_genes]
## Remove any cells that have less than threshold_gene_count
read_depth = rowSums(as.matrix(R_isog_raw))
keep_cells = read_depth >= threshold_gene_count
R_isog_raw = R_isog_raw[keep_cells, ]

metadata_isog <- metadata[metadata$X %in% rownames(R_isog_raw), ]
celltype_count = table(metadata_isog$ClusterName)
## Remove any cell types that have less than threshold_cell_count
keep_celltypes = names(celltype_count[celltype_count >= threshold_cell_count])
metadata_isog = metadata_isog[metadata_isog$ClusterName %in% keep_celltypes, ]
R_isog_selection = R_isog_raw[metadata_isog$X, ]

# Isoform LR
R_iso_raw = isoform_reference[, iso_selected_genes]
## Remove any cells that have less than threshold_gene_count
read_depth = rowSums(as.matrix(R_iso_raw))
keep_cells = read_depth >= threshold_gene_count
R_iso_raw = R_iso_raw[keep_cells, ]

metadata_iso <- metadata[metadata$X %in% rownames(R_iso_raw), ]
celltype_count = table(metadata_iso$ClusterName)
## Remove any cell types that have less than threshold_cell_count
keep_celltypes = names(celltype_count[celltype_count >= threshold_cell_count])
metadata_iso = metadata_iso[metadata_iso$ClusterName %in% keep_celltypes, ]
R_iso_selection = R_iso_raw[metadata_iso$X, ]
```

```{r}
dim(R_spatial_selection)
dim(R_isog_selection)
dim(R_iso_selection)
```



# Final aggregation by cell type to obtain input ready reference $R$.

Boxplot of the nUMI for each cell
```{r}
boxplot(metadata$nUMI, ylab = "Total gene count over cells", 
        main = "Distribution of total gene count", horizontal = T)
outliers <- boxplot.stats(metadata$nUMI)$out
threshold_count = min(outliers)
```
```{r}

# Gene SR
reference_spatial = matrix(0, ncol = ncol(R_spatial_selection), nrow = length(unique(metadata$ClusterName)))
rownames(reference_spatial) = sort(unique(metadata$ClusterName))
colnames(reference_spatial) = colnames(R_spatial_selection)


# Gene LR
reference_isog = matrix(0, ncol = ncol(R_isog_selection), nrow = length(unique(metadata$ClusterName)))
rownames(reference_isog) = sort(unique(metadata$ClusterName))
colnames(reference_isog) = colnames(R_isog_selection)


# Isoform LR
reference_iso = matrix(0, ncol = ncol(R_iso_selection), nrow = length(unique(metadata$ClusterName)))
rownames(reference_iso) = sort(unique(metadata$ClusterName))
colnames(reference_iso) = colnames(R_iso_selection)
```

# Step 1-2: Sum the count for every gene across all selected cells, which results in a vector of gene expressions for the current cell type. Keeping only the cells within the box plot so as not to generate outliers
```{r}
# Gene SR
for (i in 1:dim(metadata_spatial)[1]) {
  nUMI = metadata_spatial$nUMI[i]
  if (nUMI < threshold_count) {
    # Calculates gene specific factor metadata_spatial nUMI normalised by raw counts matrix for that given gene
    factor = nUMI/sum(R_spatial_selection[i, ])
    celltype = metadata_spatial$ClusterName[i]
    # Assign reference CT 1 gene values = factor_1 * R_spatial_selection[gene1, ] + factor_2 * R_spatial_selection[2, ] + ...
    reference_spatial[celltype,] = reference_spatial[celltype,] + R_spatial_selection[i, ] * factor
    # print(paste(sum(raw_counts[,i]*factor), nUMI))  
  }
}

# Gene LR
for (i in 1:dim(metadata_isog)[1]) {
  nUMI = metadata_isog$nUMI[i]
  if (nUMI < threshold_count) {
    # Calculates gene specific factor metadata_isog nUMI normalised by raw counts matrix for that given gene
    factor = nUMI/sum(R_isog_selection[i, ])
    celltype = metadata_isog$ClusterName[i]
    # Assign reference CT 1 gene values = factor_1 * R_isog_selection[gene1, ] + factor_2 * R_isog_selection[2, ] + ...
    reference_isog[celltype,] = reference_isog[celltype,] + R_isog_selection[i, ] * factor
    # print(paste(sum(raw_counts[,i]*factor), nUMI))  
  }
}

# Isoform LR
for (i in 1:dim(metadata_iso)[1]) {
  nUMI = metadata_iso$nUMI[i]
  if (nUMI < threshold_count) {
    # Calculates gene specific factor metadata_iso nUMI normalised by raw counts matrix for that given gene
    factor = nUMI/sum(R_iso_selection[i, ])
    celltype = metadata_iso$ClusterName[i]
    # Assign reference CT 1 gene values = factor_1 * R_iso_selection[gene1, ] + factor_2 * R_iso_selection[2, ] + ...
    reference_iso[celltype,] = reference_iso[celltype,] + R_iso_selection[i, ] * factor
    # print(paste(sum(raw_counts[,i]*factor), nUMI))  
  }
}
```

```{r}
outlierCellRemoval = function(R_selection, metadata,
                              lowerThresholdRank  = 2,
                              lowerThresholdCount = 3,
                              IQR_multiplier      = 1.5,
                              plot                = TRUE,
                              title_suffix        = "") {
  
  celltypes  = unique(metadata$ClusterName)
  keep_cells = c()
  plot_data  = data.frame()
  
  # Per-celltype summary for printing
  summary_table = data.frame(
    celltype       = character(),
    n_total        = integer(),
    n_kept         = integer(),
    n_removed      = integer(),
    upper_threshold = numeric()
  )
  
  for (ct in celltypes) {
    
    # Cells belonging to this celltype
    ct_idx   = which(metadata$ClusterName == ct)
    ct_cells = metadata$X[ct_idx]
    ct_nUMI  = metadata$nUMI[ct_idx]
    
    # ── Upper threshold: per-celltype IQR ──────────────────────────────────
    Q3              = quantile(ct_nUMI, 0.75)
    IQR_val         = IQR(ct_nUMI)
    upper_threshold = Q3 + IQR_multiplier * IQR_val
    pass_upper      = ct_nUMI <= upper_threshold
    
    # ── Lower threshold: rank-based count filter ───────────────────────────
    ct_counts  = as.matrix(R_selection[ct_cells, , drop = FALSE])
    pass_lower = apply(ct_counts, 1, function(cell_vec) {
      sorted_counts = sort(cell_vec, decreasing = TRUE)
      rank_val      = sorted_counts[min(lowerThresholdRank, length(sorted_counts))]
      rank_val >= lowerThresholdCount
    })
    
    pass_both  = pass_upper & pass_lower
    keep_cells = c(keep_cells, ct_cells[pass_both])
    
    # ── Collect plot data ──────────────────────────────────────────────────
    plot_data = rbind(plot_data, data.frame(
      cell            = ct_cells,
      nUMI            = ct_nUMI,
      celltype        = ct,
      kept            = pass_both,
      upper_threshold = upper_threshold
    ))
    
    # ── Per-celltype summary ───────────────────────────────────────────────
    summary_table = rbind(summary_table, data.frame(
      celltype        = ct,
      n_total         = length(ct_cells),
      n_kept          = sum(pass_both),
      n_removed       = sum(!pass_both),
      upper_threshold = round(upper_threshold, 2)
    ))
  }
  
  # ── Print summary table ────────────────────────────────────────────────
  cat("\n── Outlier Cell Removal Summary", title_suffix, "──\n")
  cat(sprintf("  lowerThresholdRank  = %d\n", lowerThresholdRank))
  cat(sprintf("  lowerThresholdCount = %d\n", lowerThresholdCount))
  cat(sprintf("  IQR multiplier      = %.1f\n", IQR_multiplier))
  cat(sprintf("  Total cells before  = %d\n", nrow(metadata)))
  cat(sprintf("  Total cells kept    = %d\n", length(keep_cells)))
  cat(sprintf("  Total cells removed = %d\n", nrow(metadata) - length(keep_cells)))
  cat("\nPer-celltype breakdown:\n")
  print(summary_table, row.names = FALSE)
  
  # ── Raincloud plot ─────────────────────────────────────────────────────
  if (plot) {
    
    # Threshold line data (one value per celltype)
    threshold_data = plot_data %>%
      dplyr::group_by(celltype) %>%
      dplyr::summarise(upper_threshold = unique(upper_threshold),
                       .groups = "drop")
    
    p = ggplot(plot_data, 
               aes(x = celltype, y = nUMI, fill = celltype)) +
      
      # Half-violin (density cloud)
      ggdist::stat_halfeye(
        adjust       = 0.5,
        width        = 0.6,
        .width       = 0,
        justification = -0.2,
        point_colour = NA,
        alpha        = 0.7
      ) +
      
      # Boxplot
      geom_boxplot(
        width         = 0.15,
        outlier.shape = NA,
        colour        = "black",
        fill          = "white",
        alpha         = 0.8
      ) +
      
      # Jittered points coloured by kept/removed status
      geom_jitter(
        aes(colour = kept),
        width = 0.05,
        size  = 0.6,
        alpha = 0.5
      ) +
      
      # Per-celltype upper threshold line
      geom_crossbar(
        data    = threshold_data,
        aes(x = celltype,
            y    = upper_threshold,
            ymin = upper_threshold,
            ymax = upper_threshold),
        colour    = "red",
        width     = 0.4,
        linewidth = 0.5,
        inherit.aes = FALSE
      ) +
      
      scale_colour_manual(
        values = c("TRUE"  = "#2196F3",
                   "FALSE" = "#F44336"),
        labels = c("TRUE"  = "Kept",
                   "FALSE" = "Removed"),
        name   = "Status"
      ) +
      
      coord_flip() +
      
      labs(
        title    = paste("Cell nUMI distribution by celltype", title_suffix),
        subtitle = paste0("Red line = Q3 + ", IQR_multiplier,
                          "×IQR  |  Blue = kept, Red points = removed"),
        x = "Cell Type",
        y = "nUMI (total gene count)"
      ) +
      
      theme_bw(base_size = 11) +
      theme(
        legend.position  = "bottom",
        axis.text.y      = element_text(size = 8),
        plot.title       = element_text(face = "bold"),
        plot.subtitle    = element_text(size = 9, colour = "grey40")
      ) +
      
      guides(fill = "none")  # suppress redundant fill legend
    
    print(p)
  }
  
  return(keep_cells)
}

# Gene SR
keep_spatial     = outlierCellRemoval(R_spatial_selection, metadata_spatial,
                                      title_suffix = "(Gene SR)")
R_spatial_selection = R_spatial_selection[keep_spatial, ]
metadata_spatial    = metadata_spatial[metadata_spatial$X %in% keep_spatial, ]

# Gene LR
keep_isog        = outlierCellRemoval(R_isog_selection, metadata_isog,
                                      title_suffix = "(Gene LR)")
R_isog_selection = R_isog_selection[keep_isog, ]
metadata_isog    = metadata_isog[metadata_isog$X %in% keep_isog, ]

# Isoform LR
keep_iso         = outlierCellRemoval(R_iso_selection, metadata_iso,
                                      title_suffix = "(Isoform LR)")
R_iso_selection  = R_iso_selection[keep_iso, ]
metadata_iso     = metadata_iso[metadata_iso$X %in% keep_iso, ]
```


# Step 3: Normalize this vector so that the sum is 1. Completing this step yields a single row in the input-ready reference R.

```{r}
# Removing Cell Types with 0 rowSums in references
reference_spatial = reference_spatial[names(which(rowSums(reference_spatial) > 0)),]
reference_isog = reference_isog[names(which(rowSums(reference_isog) > 0)),]
reference_iso = reference_iso[names(which(rowSums(reference_iso) > 0)),]

laplace_smooth = function(ref_matrix, epsilon = 1) {
  smoothed = ref_matrix + epsilon
  return(smoothed)
}

reference_spatial = laplace_smooth(reference_spatial)
reference_isog    = laplace_smooth(reference_isog)
reference_iso     = laplace_smooth(reference_iso)

# Normalise each matrix to have rowSum = 1
reference_spatial = reference_spatial / rowSums(reference_spatial)
reference_isog = reference_isog / rowSums(reference_isog)
reference_iso = reference_iso / rowSums(reference_iso)

# Sanity checks
cat("Spatial ref  — min:", min(reference_spatial),
                  "zeros:", sum(reference_spatial == 0), "\n")
cat("Isog ref     — min:", min(reference_isog),
                  "zeros:", sum(reference_isog == 0), "\n")
cat("Iso ref      — min:", min(reference_iso),
                  "zeros:", sum(reference_iso == 0), "\n")
```

Filtering isoform_dict to keep only the significant isoforms

```{r}
kept_isoform = colnames(C_iso_selection)

isoform_dict_filtered = list()
for (isoform_fullname in kept_isoform){
  parts = strsplit(isoform_fullname, split = "\\.\\.")[[1]]
  gene = parts[1]
  iso = parts[2]
  
  isoform_dict_filtered[[gene]] = c(isoform_dict_filtered[[gene]], iso)
}
  
  
```


# Creating prior constant weight $b_k$
```{r}
pw_constant = 0.1

pw_spatial = rep(pw_constant, dim(reference_spatial)[1])
pw_isog = rep(pw_constant, dim(reference_isog)[1])
pw_iso = rep(pw_constant, dim(reference_iso)[1])

saveRDS(pw_spatial, "/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Data/Isoform/LebrigandIsoform/proc_data_pipeline/gene_SR_pw.rds")
saveRDS(pw_isog, "/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Data/Isoform/LebrigandIsoform/proc_data_pipeline/gene_LR_pw.rds")
saveRDS(pw_iso, "/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Data/Isoform/LebrigandIsoform/proc_data_pipeline/iso_LR_pw.rds")
```

# Save all C and R matrices now as processed data
```{r}
# Gene SR
saveRDS(C_spatial_selection, "/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Data/Isoform/LebrigandIsoform/proc_data_pipeline/gene_SR_spatial.rds")
saveRDS(reference_spatial, "/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Data/Isoform/LebrigandIsoform/proc_data_pipeline/gene_SR_ref.rds")


# Gene LR
saveRDS(C_isog_selection, "/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Data/Isoform/LebrigandIsoform/proc_data_pipeline/gene_LR_spatial.rds")
saveRDS(reference_isog, "/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Data/Isoform/LebrigandIsoform/proc_data_pipeline/gene_LR_ref.rds")


# Isoform LR
saveRDS(C_iso_selection, "/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Data/Isoform/LebrigandIsoform/proc_data_pipeline/iso_LR_spatial.rds")
saveRDS(reference_iso, "/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Data/Isoform/LebrigandIsoform/proc_data_pipeline/iso_LR_ref.rds")
saveRDS(isoform_dict_filtered, "/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Data/Isoform/LebrigandIsoform/proc_data_pipeline/iso_LR_dict.rds")
```

