---
title: "LebIsoform_FlexiDeconv_Analysis"
output: pdf_document
date: "2026-02-01"
---


# Import libraries

```{r}
set.seed(1)
library(bayess)
library(STdeconvolve)
library(Matrix)
source("../functions(new).R")
```

# Read VI output
Epsilon iteration:
Time taken for computation: 40289 seconds ~ 11 hour 15 minutes
Number of iterations: 3720

Log space iteration:
Time taken for computation: 31355 seconds ~ 8 hours 42 minutes
Number of iterations: 860
```{r}
# result = readRDS("/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Outputs/initialOutput_LogSpace.rds")
result = readRDS("/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Outputs/report_results/pw_2.0/gene_LR_pw_2.0_t1.rds")
spatial = readRDS("/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Data/Isoform/LebrigandIsoform/proc_data_pipeline/iso_LR_spatial.rds")
reference = readRDS("/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Data/Isoform/LebrigandIsoform/proc_data_pipeline/iso_LR_ref.rds")
isoform_dict = readRDS("/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Data/Isoform/LebrigandIsoform/proc_data_pipeline/iso_LR_dict.rds")
prior_constant_data = readRDS("/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Data/Isoform/LebrigandIsoform/proc_data_pipeline/iso_LR_pw.rds")
meta = readRDS("/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Data/Isoform/LebrigandIsoform/mob_metadata.rds")
summary(result)
```


# Data Analysis
```{r}
deconv_res = result$gamma/rowSums(result$gamma)
colors_provide = rep("black", ncol(deconv_res))
names(colors_provide) = colnames(deconv_res)
pos = data.frame(x = meta[rownames(deconv_res),]$imagecol, 
                 y = 50000 - meta[rownames(deconv_res),]$imagerow)
rownames(pos) = rownames(deconv_res)
for (i in 1:ncol(deconv_res)) {
  new_col = colors_provide
  new_col[i] = 'red'
  p = vizTopic(as.matrix(deconv_res), pos=pos, size=2, topic = i, plotTitle = names(colors_provide)[i])
  plot(p)
}

```

```{r, fig.width=10, fig.height=8, out. Width="100%"}
# colors_provide = rep('black', ncol(result$gamma))
# names(colors_provide) = colnames(result$gamma)
# colors_provide["N11"] = 'green'
# colors_provide["N14"] = 'blue'
# colors_provide["N10"] = 'red'

# colors_provide = rep('black', ncol(result$gamma))
# names(colors_provide) = colnames(result$gamma)
# colors_provide["Astro1"] = 'brown'
# colors_provide["N10"] = 'red'
# colors_provide["N11"] = 'green'
# colors_provide["N12"] = 'darkorange'
# colors_provide["OEC1"] = 'steelblue'
# colors_provide["N14"] = 'blue'
# colors_provide["OEC5"] = 'magenta'
# colors_provide["N5"] = 'cyan'
# colors_provide["N13"] = 'yellow'
# colors_provide["N15"] = 'indianred1'
# colors_provide["RBCs"] = 'deepskyblue'
# colors_provide['Mono'] = 'cadetblue1'
# colors_provide['MicroG1'] = 'purple4'
# colors_provide['N4'] ='coral3'
# colors_provide['OEC1'] = 'gold'
# colors_provide['OEC2'] = 'purple'
# colors_provide['MyOligo'] = 'hotpink'


colors_provide = rep('black', ncol(result$gamma))
names(colors_provide) = colnames(result$gamma)
colors_provide['Astro1'] = 'coral3'
colors_provide['Astro2'] = 'coral'
colors_provide['EC1'] = 'bisque'
colors_provide['EC2'] = 'bisque4'
colors_provide['Mes1'] = 'chartreuse4'
colors_provide['Mes2'] = 'chartreuse'
colors_provide['MicroG1'] = 'purple4'
colors_provide['MicroG2'] = 'purple2'
colors_provide['MicroG3'] = 'purple'
colors_provide['Mono'] = 'cadetblue1'
colors_provide['Mural1'] = 'gold4'
colors_provide['Mural2'] = 'gold1'
colors_provide['MyOligo'] = 'brown'
colors_provide['Mφ'] = 'lemonchiffon'
colors_provide['N1'] = 'grey1'
colors_provide['N2'] = 'grey10'
colors_provide['N3'] = 'grey20'
colors_provide['N4'] ='grey30'
colors_provide['N5'] = 'grey40'
colors_provide['N8'] = 'grey50'
colors_provide['N10'] = 'grey60'
colors_provide['N11'] = 'grey70'
colors_provide['N12'] = 'grey80'
colors_provide['N13'] = 'grey90'
colors_provide['N14'] = 'grey100'
colors_provide['N15'] = 'lavender'
colors_provide['N16'] = 'linen'
colors_provide['OEC1'] = 'hotpink'
colors_provide['OEC2'] = 'hotpink3'
colors_provide['OEC3'] = 'indianred1'
colors_provide['OEC4'] = 'indianred4'
colors_provide['OEC5'] = 'red'
colors_provide['OPC'] = 'blue'
colors_provide['RBCs'] = 'cyan'

# svg("/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Figures/gene_LR_cellTypeDeconvolution.svg", width = 800, height = 600)
visAllTopics(as.matrix(deconv_res), pos = pos, topicCols = colors_provide, r = 120, plotTitle = "Gene SR ")
# dev.off
```
```{r}
result_gene = readRDS("/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Outputs/report_results/pw_2.0/gene_LR_pw_2.0_t1.rds")

result_t2 = readRDS("/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Outputs/report_results/pw_2.0/Output_LogSpace_pw_2.0_t2.rds")

result_assisted = readRDS("/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Outputs/report_results/pw_2.0/Output_LogSpace_pw_2.0_assistGamma.rds")

deconv_res_gene = result_gene$gamma / rowSums(result_gene$gamma)
deconv_res_t2 = result_t2$gamma / rowSums(result_t2$gamma)
deconv_res_assisted = result_assisted$gamma / rowSums(result_assisted$gamma)

library(patchwork)

p1 <- visAllTopics(
  as.matrix(deconv_res_gene), 
  pos = pos, 
  topicCols = colors_provide, 
  r = 120, 
  plotTitle = "Gene SR",
  showLegend = FALSE  # removes legend on left plot
)

p2 <- visAllTopics(
  as.matrix(deconv_res_t2), 
  pos = pos, 
  topicCols = colors_provide, 
  r = 120, 
  plotTitle = "Isoform LR (Assisted)"
)

# Combine with (a) and (b) labels
combined <- p1 + p2 + 
  plot_annotation(tag_levels = 'a',          # labels as (a), (b)
                  tag_prefix = '(',
                  tag_suffix = ')') &
  theme(plot.tag = element_text(size = 12, face = "bold"))

# Save
# svg("/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Figures/report/gene+iso_t2_celltypedeconvolution.svg", width = 16, height = 7)
# print(combined)
# dev.off()

rsvg_pdf("/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Figures/report/gene+iso_t2_celltypedeconvolution.svg", "/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Figures/report/gene+iso_t2_celltypedeconvolution.pdf", width = 3200, height = 1400)

```


```{r}
# Compute abundance dataframes
compute_abundance <- function(deconv_res, title) {
  celltypeimportance <- colSums(deconv_res)
  importance_df <- data.frame(
    CellType   = names(celltypeimportance),
    Proportion = celltypeimportance / sum(celltypeimportance)
  )
  importance_df <- importance_df[order(importance_df$Proportion, decreasing = TRUE), ]
  importance_df$CellType <- factor(importance_df$CellType, levels = importance_df$CellType)
  importance_df$title <- title
  return(importance_df)
}
df_gene <- compute_abundance(deconv_res_gene, "Gene SR")
df_t2   <- compute_abundance(deconv_res_t2,   "Isoform LR")
# Base colour mapping on gene result ordering
all_celltypes <- levels(df_gene$CellType)
shared_colors <- setNames(colors_provide[seq_along(all_celltypes)], all_celltypes)
# Plot function
plot_abundance <- function(df, show_legend = FALSE) {
  ggplot(df, aes(x = CellType, y = Proportion, fill = CellType)) +
    geom_bar(stat = "identity") +
    scale_fill_manual(values = shared_colors) +
    labs(
      title = unique(df$title),
      y     = "Proportion",
      x     = "Cell Type"
    ) +
    theme_minimal() +
    theme(
      axis.text.x     = element_text(angle = 90, hjust = 1, size = 7),
      plot.title      = element_text(hjust = 0.5, face = "bold"),
      legend.position = ifelse(show_legend, "right", "none")
    )
}
p1 <- plot_abundance(df_gene, show_legend = FALSE)
p2 <- plot_abundance(df_t2,   show_legend = TRUE)
# Combine
combined <- p1 + p2 +
  plot_annotation(tag_levels = 'a',
                  tag_prefix  = '(',
                  tag_suffix  = ')') &
  theme(
    plot.tag          = element_text(size = 12, face = "bold"),
    plot.tag.position = c(0, 1)
  )
# Save
# svg("/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Figures/report/gene+iso_t2_abundance.svg",
#     width = 14, height = 6)
print(combined)
# dev.off()

```


# Plot by decreasing frequency
```{r}
est_spatial_abundance = result$gamma/rowSums(result$gamma)
celltypeimportance <- colSums(est_spatial_abundance)
importance_df <- data.frame(
  CellType = names(celltypeimportance),
   Proportion = celltypeimportance / sum(celltypeimportance)
)

# Sort by proportion (descending)
importance_df <- importance_df[order(importance_df$Proportion, decreasing = TRUE), ]

# Ensure factor levels match sort order
importance_df$CellType <- factor(importance_df$CellType, levels = importance_df$CellType)

# Plot
ggplot(importance_df, aes(x = CellType, y = Proportion, fill = CellType)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = scales::percent(Proportion, accuracy = 0.1)), 
            vjust = -0.3, size = 2.5) +
  labs(
    title = "Ground Truth Relative abundance of cell types",
    y = "Proportion",
    x = "Cell Type"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1)
  )
```


# Gene expression analysis
```{r}
set.seed(27)

# sampled_rows <- sample(1:nrow(reference), size = 5)
sampled_rows = which(rownames(reference) %in% c("N16", "N10", "OEC1", "EC1", "N15", "N6", "OPC"))
sampled_cols <- sample(1:ncol(reference), size = ncol(reference))  # adjust size as needed
celltype_names = rownames(reference)

comparison_matrix <- matrix(0, nrow = 2*length(sampled_rows), ncol = length(sampled_cols))
idx <- 1
for (i in sampled_rows) {
  comparison_matrix[idx,]   <- reference[i, sampled_cols] / sum(reference[i, sampled_cols])
  comparison_matrix[idx+1,] <- result$tau[i, sampled_cols] / sum(result$tau[i, sampled_cols])
  idx <- idx + 2
}

# # Optional: label rows with sampled row indices for clarity
rownames(comparison_matrix) <- as.vector(rbind(
  paste0("Reference: ",        celltype_names[sampled_rows]),
  paste0("Estimated: ", celltype_names[sampled_rows])
))

# colnames(comparison_matrix) <- colnames(reference)[sampled_cols]

visualize_reference(comparison_matrix, want_log = F, cluster_col = F, cluster_row = T)
```

Comparison of similarities between different named cell types for gene expression analysis

```{r}
# set.seed(27)
# 
# result_gene = readRDS("/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Outputs/report_results/pw_2.0/gene_LR_pw_2.0_t1.rds")
# 
# result_t2 = readRDS("/data/gpfs/projects/punim0614/ashtonl/FlexiDeconv/Isoform_Work/Outputs/report_results/pw_2.0/Output_LogSpace_pw_2.0_t2.rds")
# 
# # sampled_rows <- sample(1:nrow(reference), size = 5)
# # sampled_rows = which(rownames(reference) %in% c("N16", "N10", "OEC1", "EC1", "N15", "N6", "OPC"))
# sampled_row_genes = which(rownames(reference) %in% assistedtop5)
# sampled_row_t2 = which(rownames(reference) %in% t2_top5)
# sampled_cols <- sample(1:ncol(reference), size = ncol(reference))  # adjust size as needed
# celltype_names = rownames(reference)
# 
# comparison_matrix <- matrix(0, nrow = 3*length(sampled_row_genes), ncol = length(sampled_cols))
# idx <- 1
# # for (i in sampled_rows) {
# #   comparison_matrix[idx,]   <- reference[i, sampled_cols] / sum(reference[i, sampled_cols])
# #   comparison_matrix[idx+1,] <- result$tau[i, sampled_cols] / sum(result$tau[i, sampled_cols])
# #   idx <- idx + 2
# # }
# 
# for (i in 1:length(sampled_row_genes)) {
#   comparison_matrix[idx,]   <- reference[i, sampled_cols] / sum(reference[i, sampled_cols])
#   comparison_matrix[idx+1,] <- result_gene$tau[sampled_row_genes[i], sampled_cols] / sum(result_gene$tau[sampled_row_genes[i], sampled_cols])
#   comparison_matrix[idx+2,] <- result_t2$tau[sampled_row_t2[i], sampled_cols] / sum(result_t2$tau[sampled_row_t2[i], sampled_cols])
#   idx <- idx + 3
# }
# 
# # # Optional: label rows with sampled row indices for clarity
# # rownames(comparison_matrix) <- as.vector(rbind(
# #   paste0("Reference: ",        celltype_names[sampled_rows]),
# #   paste0("Estimated: ", celltype_names[sampled_rows])
# # ))
# 
# # Optional: label rows with sampled row indices for clarity
# rownames(comparison_matrix) <- as.vector(rbind(
#   paste0("Reference: ",        celltype_names[sampled_row_genes]),
#   paste0("Gene estimated: ", celltype_names[sampled_row_genes]),
#   paste0("Iso estimated: ", celltype_names[sampled_row_t2])
# ))
# 
# # colnames(comparison_matrix) <- colnames(reference)[sampled_cols]
# 
# visualize_reference(comparison_matrix, want_log = F, cluster_col = F, cluster_row = T)
```




